---
title: "A2Three"
author: "ruchika"
---

## MOVIE PROFITS {style="COLOR:BLUE"}

```{r}
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
```

```{r}
movie_profit_data <- read_delim("../../data/movie_profit.csv")
delim =";"
glimpse(movie_profit_data)
```

```{r}
inspect(movie_profit_data)
```

```{r}
skim(movie_profit_data)
```

#### DATA DICTIONARY

-   There are 10 variables altogether -

-   release-date - is a quant variable since all the movies have different dates.

-   movie - its a qual variable

-   distributor - again is a qual variable

-   mpaa_rating - is a qual variable

-   genre - is a qual variable since it can be grouped

-   production_budget - is a quant varible since it shows the budget of the movie

-   domestic_gross - is a quant variable.

-   worldwide_gross -is a quant variable.

-   profit_ratio -is a quant variable.

-   decade -is a quant variable.

    #### HYPOTHESIS

    -   Higher production budgets are positively correlated with higher revenues.

    -   Movies categorized as Action or Adventure genres have significantly higher worldwide gross earnings compared to other genres like Drama or Romance as they connect to larger audience.

    -   Animated movies will have a higher profit ratio compared to live-action movies.

    -   There is no significant difference in average domestic gross earnings between films distributed by major studios and those distributed by independent/smaller studios.

    <!-- -->

    -   Below, will be mutating some variables to convert into factor

```{r}
movie_modified <- movie_profit_data %>% 
  mutate(
    distributor = as.factor(distributor),
    mpaa_rating = as.factor(mpaa_rating),
    genre = as.factor(genre),
    decade = as.factor(decade)
  )

glimpse(movie_modified)
print(movie_modified)
```

```{r}
movie_modified %>%
  group_by(distributor, genre) %>%                 
  
  summarise(median_profit_ratio = median(profit_ratio, na.rm = TRUE)) %>%  
  ggplot(aes(x = genre, y = median_profit_ratio)) +  
  geom_bar(stat = "identity", fill = "darkgray") +   
  facet_wrap(~ distributor) +                        
  coord_flip() +                                     
  labs(
    title = "Profits made by Film Distributors",
    subtitle = "Ratio of Profits to Budgets",
    x = "Genre", 
    y = "Median Profit Ratio",
    caption = "Tidy Tuesday Oct 23, 2018"
  ) 
```

#### QUESTIONS

-   How does the genre of a movie influence its profits?

-   Is there a significant difference in profit ratios among movies with different MPAA ratings?

-   Do movies released by major distributors perform better in terms of domestic gross compared to independent distributors even if its the same genre?

#### INFERENCES

-   20Tth Century Fox shows a relatively balanced profit ratio across genres, with action and adventure movies generating slightly higher profits compared to other genres (maybe cause its more renowned).

-   Other distributors also show a more balanced distribution, though none of the genres seem to dominate the profits significantly.

-   Across most distributors, action & adventure films tend to dominate in terms of profit ratio.

-   Horror & drama movies consistently show lower profits compared to other genres.
