---
title: "Class3"
author: "ruchika"
format: html
editor: visual
---

```{r}
#| label : setup

library(tidyverse)
library(mosaic)
library(ggformula)
library(skimr)
```

#gg(grammar of graphics), viridis - colours that we get from the gg package

```{r}
taxi <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/modeldata/taxi.csv")
taxi
```

#Data munging - mutating, ordered - is basically putting the data according to the specific order instead of alphabetical order.

```{r}
## Convert `dow`, `local`, and `month` into ordered factors
taxi_modified <- taxi %>%
  mutate(
    dow = factor(dow,
      levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      labels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      ordered = TRUE
    ),
    ##
    local = factor(local,
      levels = c("no", "yes"),
      labels = c("no", "yes"),
      ordered = TRUE
    ),
    ##
    month = factor(month,
      levels = c("Jan", "Feb", "Mar", "Apr"),
      labels = c("Jan", "Feb", "Mar", "Apr"),
      ordered = TRUE
    )
  )
taxi_modified %>% glimpse()
```

#So the tip is on the x-axis, count on y-axis which I don't need to take care of since it's plotted by gf_bar, and colour is local. From this data, one could say that non-local trips are tipped the most. Hypothesis could be - maybe local trips are very short distance, thus passengers don't feel the need to tip OR non-local tip the most because they come to that area as a tourist and are having a fun time thus tip better.

```{r}

##
taxi_modified %>%
  gf_bar(~tip,
    fill = ~local,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart")
```

\# 3 Types of Positions - fill (becomes 100% and is proportionally based), stack (one over another), dodge (side by side)

```{r}

##
taxi_modified %>%
  gf_bar(~local,
    fill = ~tip,
    position = "fill"
  ) %>%
  gf_labs(
    title = "Plot 2B: Stacked Bar Chart",
    subtitle = "Can we spot per group differences in proportions??"
  )
```

#hjust is horizontal justification, basically position of the text written on x-axis, angle of the same.

```{r}

##
taxi_modified %>%
  gf_bar(~company,
    fill = ~tip,
    position = "fill"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart") %>%
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

#Can say tips are given the most at 2/4 am. Hypothesis could be, it's a time that most passengers feel unsafe (can see many aspects women being unsafe, people being unsafe since many accidents occur at this hour) thus after having a normal, safe ride they feel the need to tip more for their.

```{r}
## Set graph theme
# theme_set(new = theme_custom())
##
gf_bar(~hour, fill = ~tip, data = taxi_modified, position = "fill" ) %>%
  gf_labs(title = "Plot B: Counts of Tips by Hour")
```

#Sunday is the most tips cause SUNDAY IS FUNDAY.

```{r}
##
gf_bar(~dow, fill = ~tip, position ="fill", data = taxi_modified) %>%
  gf_labs(title = "Plot C: Counts of Tips by Day of Week")#
```

#April has the most tips

```{r}
##
gf_bar(~month, fill = ~tip,position ="fill", data = taxi_modified) %>%
  gf_labs(title = "Plot D: Counts of Tips by Month")
```

#Monday,Tue,Wed,Thu of April has most tips.

```{r}
##
gf_bar(~ month | dow, fill = ~tip, data = taxi_modified, position ="fill") %>%
  gf_labs(title = "Plot E: Counts of Tips by Day of Week and Month")
```

```{r}
##
## This may be too busy a graph...
gf_bar(~ dow , fill = ~tip, data = taxi_modified, position = "fill") %>%
  gf_labs(
    title = "Plot F: Counts of Tips by Hour and Day of Week",
    subtitle = "Is this plot arrangement easy to grasp?"
  )
```

## APARTMENT DATA (Your Turn)

```{r}
Fertility <- read_csv("../../data/Fertility.csv")
Fertility
```

#Turned to factor since they can be categorized, eg - yes/no , male/female

```{r}
Fertility_modified <- Fertility %>% dplyr::mutate(
  morekids = as_factor(morekids),
  gender1 = as_factor(gender1),
  gender2 = as_factor(gender2),
  afam = as_factor(afam),
  hispanic = as_factor(hispanic),
  other = as_factor(other)
)

glimpse(Fertility_modified)
```

#So showcases how male bars are generally taller thus indicating a male-dominant trends in those age groups

```{r}
##
Fertility_modified %>%
  gf_bar(~age,
    fill = ~gender2,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 1:AGE AND GENDER2")
```

#Showcases how number of hispanic people is lesser than number of hispanic people who want kids whereas it opposite in non-hispanic people.

```{r}
Fertility_modified %>%
  gf_bar(~hispanic,
    fill = ~morekids,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 1:AGE AND GENDER2")
```

#After a certain age, there is a decline in wanting kids (32-35) also there is an initial decline during the age of 20-24

```{r}
Fertility_modified %>%
  gf_bar(~age,
    fill = ~morekids,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 1:AGE AND GENDER2")
```
