---
title: "A2TWO"
author: "ruchika"
---

## GENDER AT THE WORK PLACE {style="color: blue"}

```{r}
#| label: setup

library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
```

```{r}
job_gender_data <- read_delim("../../data/job_gender_data.csv")
delim =";"
glimpse(job_gender_data)
```

-   This dataset contains 12 variables -

-   Year - since it is consistent (2016), it's a quant variable

-   Occupation - since it showcases a range of different fields its, qual variable.

-   major_category - qual

-   minor_category - qual

-   total_workers - quant

-   workers_male - quant

-   workers_female - quant

-   percent_female - quant

-   total_earnings- quant

-   total_earnings_male - quant

-   total_earnings_female - quant

-   wage_percent_of_male - quant

#### HYPOTHESIS-

-   There is no significant difference in total earnings between male and female workers across all occupations.

-   OR

-   Female workers earn significantly less than male workers across most occupations.

-   Certain major categories of occupations have a significantly higher percentage of female workers compared to others.

#### QUESTIONS -

-   Does the percentage of females have a significant impact on total earnings?

-   Is there a particular threshold of female percentage where the decline in earnings becomes more significant?

-   Does a higher percentage of females correlate with lower total earnings in all industries or sectors?

#### DATA DICTIONARY

```{r}
data_dictionary <- data.frame(
  Variable_Name = c("year"),
  Data_Type = c(""),
  Description = c("Country Name")
)

print(data_dictionary)
```

```{r}
#df <- df %>%
  #mutate(percent_male = 100 - percent_female)
# Used chatgpt to see if I can change the percentage of male workers, code didnt work
```

```{r}
job_gender_data %>%
  gf_point(total_earnings ~ percent_female) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Life Expectancy Across Countries & Years"
  )
```

```{r}
job_gender_data %>%
  gf_point(total_earnings ~ percent_female, 
           size = ~ total_workers,  
           shape = 21, 
           fill = "blue",
           alpha = 0.8) %>% 
  gf_lm() %>%
  gf_labs(
    title = "Salaries and Gender Proportion in the Workforce",
    subtitle = "Total Earnings vs Percentage of Female Workers"
  )

```

```{r}
colnames(job_gender_data)
```

#### INFERENCES

-   As the percentage of females increases, the total earnings tends to decrease,thus showing a negative corelation.

-   There is a wide range of earnings for different data points, indicating variability across the observations.,some data points have significantly higher earnings, but these are less frequent.

-   Again, here there are some outliers earning very high or very low..
